State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-11-08 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Section 7 edited, and first full page saved.

Based on~\cite{JungEtAl2022}, tool utilization for MI
software has much in common with tool utilization for ocean modelling software.
Both use tools for editing, compiling, code management, testing, building, and
project management.  From the data available, ocean modelling differs from MI
software in its use of Kanban boards for project management.

@@

We answer research question \rqref{RQ_CompareMethodologies} by comparing the
principles, processes, and methodologies used for MI software to what can be
gleaned from the literature on research software in general. In our interviews
with developers the responses about development model were vague, with only two
interviewees following a definite development model. In some cases the
interviewees felt their process was similar to an existing development model.
Three teams (about 38\%) either followed agile, or something similar to agile.
Two teams (25\%) either followed a waterfall process, or something similar.
Three teams (about 38\%) explicitly stated that their process was undefined or
self-directed.

Our observations of an informally defined process, with elements of agile
methods, matches observations for research software in general.
Scientific developers naturally use an agile philosophy \cite{AckroydEtAl2008,
CarverEtAl2007, EasterbrookAndJohns2009, Segal2005, HeatonAndCarver2015}, or an
amethododical process \cite{Kelly2013}, or a knowledge acquisition driven
process \cite{Kelly2015}.  A waterfall-like process can work for research
software \cite{Smith2016}, especially if the developers work iteratively and
incrementally, but externally document their work as if they followed a
rationale design process \cite{parnas1986rational}.

No interviewee introduced any strictly defined project management process. The
most common approach was following the issues, such as bugs and feature
requests. The \textit{3D Slicer} team had weekly meetings to
discuss the goals for the project. The \textit{INVESALIUS 3} team relied on the
GitHub process for their project management while the \textit{ITK-SNAP} team had a
fixed six-month release pace. Only the interviewee from \textit{OHIF} 
mentioned the team having a project manager. The \textit{3D Slicer} team and
\textit{BioImage Suite Web} team do nightly builds and tests. The \textit{OHIF}
developer believes that a better project management process can improve junior
developer efficiency while also improving internal and external communication.

We identified the use of unit testing in less than half of the 29 projects even
though the interviewees believed that testing (including usability tests with
users) was the top approach to improve correctness, usability, and
reproducibility.  This level of testing matches what was observed for LBM
software [citation redacted for blind review]
%\cite{Michalski2021} 
and is apparently greater than the level of
testing for ocean modelling software \cite{JungEtAl2022}.

Interviewees from all of the eight projects thought that documentation was
essential to their projects, and most of them (7 of 8) said that it could save
their time to answer questions from users and developers. Half of them (4 of 8)
saw the need to improve their documentation, and only three of them thought that
their documentations conveyed information clearly enough.

As Table~\ref{Tbl_Guidelines} suggests, an emphasis on documentation, especially
for new developers, is echoed in research software guidelines. Multiple
guidelines recommend a document explaining how to contribute to a project, often
named CONTRIBUTING. Guidelines also recommend tutorials, user guides and quick
start examples. Smith and Roscoe \cite{SmithAndRoscoe2018} suggest including instructions
specifically for on-boarding new developers. For open-source software in general
(not just research software), \cite{Fogel2005} recommends providing tutorial
style examples, developer guidelines, demos, and screenshots.

>>>>

Based on~\cite{JungEtAl2022}, tool use for MI
software is similar to tool use for ocean modelling software.
Both use tools for editing, compiling, code management, testing, building, and
project management, but differ
in the latter's use of Kanban boards for project management.

@@

In our interviews, developers' responses to questions about development model
were vague, with only two interviewees following a definite model, with others
feeling their process was ``similar'' to an existing model.  Three teams
followed agile or alike, two teams  followed waterfall or alike, and three
teams explicitly stated that their process was undefined or self-directed.

This matches observations for research software in general.
Scientific developers naturally use an agile philosophy \cite{AckroydEtAl2008,
CarverEtAl2007, EasterbrookAndJohns2009, Segal2005, HeatonAndCarver2015}, or an
amethododical process \cite{Kelly2013}, or a knowledge acquisition driven
process~\cite{Kelly2015}.  A waterfall-like process can work for research
software~\cite{Smith2016}, especially if the developers work iteratively and
incrementally, but externally document their work as if they followed a
rational design process~\cite{parnas1986rational}.

No interviewee mentioned a strictly defined project management process. 
% JC: I don't think this level of per-project detail makes sense in this
% review article - it should be about stats and trends, not reporting on
% minute details. We could refer the reader to Ao's thesis for the details.
% 
% The
% most common approach was following the issues, such as bugs and feature
% requests. The \textit{3D Slicer} team had weekly meetings to discuss
% the goals for the project. The \textit{INVESALIUS 3} team relied on the
% GitHub process for their project management while the \textit{ITK-SNAP} 
% team had a fixed six-month release pace. Only the interviewee from 
% \textit{OHIF} 
% mentioned the team having a project manager. The \textit{3D Slicer} team and
% \textit{BioImage Suite Web} team do nightly builds and tests. The \textit{OHIF}
% developer believes that a better project management process can improve junior
% developer efficiency while also improving internal and external communication.

Less than half of the projects used unit testing, even
though the interviewees believed that testing (including usability tests) was
the top approach to improve correctness, usability, and reproducibility.  This
level of testing matches what was observed for LBM
software [citation redacted for blind review]
%\cite{Michalski2021} 
and is apparently greater than the level of
testing for ocean modelling software~\cite{JungEtAl2022}.

All Interviewees thought that documentation was
essential to their projects, and most of them (7 of 8) said that it could save
their time to answer questions from users and developers. Half of them (4 of 8)
saw the need to improve their documentation, and only three of them thought that
their documentations conveyed information clearly enough.
